Investigating the Gaussianity of Supernova SALT2 Summary Statistics

### 2016-08-03 dessn/investigations/gaussianity/paper/gaussianity.tex
Unfortunately having some difficulty fitting

SALT2.

Previous studies using summary statistics and their data sets.

@@

\section{Next Section}
Think of section title

Supernova models, summary statistics, why they are used (instead of light curve data), and the fitting methodologies that have been used in the past to get summary statistics.

\section{Next section}

@@

 compare the different methods

@@

@@

\bibliographystyle{mnras}
\bibliography{bibliography} % if your bibtex file is called example.bib

@@

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

>>>>

@@

\section{Motivation}

SALT2 and other models

why summary stats are used (instead of light curve data)

fitting methodologies

highlight Previous studies using summary statistics and their data sets.

\section{Methodology}

@@

state skewness introduced as z increases and ston decreases

which creates difference when between mean and max likelihood

@@

\section{Cosmological Impact}

Fit cosmology against simulated SN

Do for des shallow and deep, using survey area to produce z dist plus extra low-z sample (0.05<z<0.2). simulate from light curves, apply selection effect of ston>5to cull bad fits. have <x> shallow.

toy cosmology model. adopt $\alpha$ and $\beta$ values for Phillips correction from Betoule2014, assume known gaussian intrinsic scatter, have $\Omega_m$, $w$ and $M_B$ as cosmology parameters - marginalise over $M_B$.

Show cosmology results.

@@

\bibliographystyle{mnras}
\bibliography{bibliography}

@@

%\appendix
%\section{Some extra material}
%If you want to present additional material which would interrupt the flow of the main paper, it can be placed in an Appendix which appears after the list of references.
